---
title: "esm206_lab8"
author: "Matthew McCafferty"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelsummary)
library(broom)
library(here)
library(corrplot)
```

### Read in slo homes data

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```
### Create a subset with four cities (homes subset) onkly contains observations for 

-"San luis Obispo"
-"Atascadero"
-"Arroyo Grande"
-"Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande","Santa Maria-Orcutt"))

```

### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sales status

```{r, include=FALSE}
homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean = mean(Price),
            sd= sd(Price))

```


Task: Explore relationship between square footage and homes price in a scatterplot

```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point() +
  theme_minimal() +
  geom_smooth(method = "lm")
```


### Try a few linear models 

Use multiple linear regression to investigate relationships between several predictor variables and home price.

Create 2 different permutations of this model
(1) City, bedrooms, bathrooms, Sqft, Status
(2) price~ Coty Sqft, Status
(3) Try another one (lm3)

```{r}
lm_1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)

lm_2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)

lm_3 <- lm(SqFt ~ Price + Status, data = homes_subset)

summary(lm_1)

# If I wanted San Luis Obispo to be the reference level:
#Use fct_relevel to specify a new reference level

new_homes_subset<- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo")) 

lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)

summary(lm_slo)
```
### R^2 Almost 54% of variance in home price is explained by this model


### Explore correlations between quantitative variables 

Make a subset called homes_quat starting with homes subset that only contains proce Sqft

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)


corrplot(homes_cor, method = "ellipse")
```

### Compare AIC values

```{r}
AIC(lm_1)
AIC(lm_2)
```
### Model Summary to return multiple model outputs

```{r}
modelsummary(list(lm_1, lm_2, lm_3))
```

### Check out Diagnostic plots for lm_1

```{r}
plot(lm_1)
```
### Use Broom:: augment to return the predictions for existing observations

```{r}
home_predictions <- augment(lm_1)

ggplot(data = home_predictions, aes(x=.resid)) +
  geom_histogram()
```

